Dynamic Knapsack Problem

### 2021-08-25 v2-Manuscript/sections/adp_model.tex
working on adding a priority index

\begin{alignat}{10}
	& \beta^{0}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} (1 - \gamma) = 1 \\
	& \beta^{ul}: 
		&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ul_{p} - 
		\gamma (\hat{ul}_{p}) \Big) \ge E[ul_{p}] 
		&&	\forall p \in p\_co \\ 
	&	
		&& 	\sum_{\vec{S}\vec{A}}\vec{w} ( ul_{p}) \ge E[ul_{p}]
		&&	\forall p \in p\_nco \\
	&	\beta^{pw}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{0dkc} - 
		\gamma (pea_{dkc}) \Big) \ge E[ps_{0dkc}]
		&&	\forall dkc \\
	&	
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdkc} - 
		\gamma (\hat{pw}_{m-1dkc}) \Big) \ge E[pw_{mdkc}]
		&&	\forall m \in \{1...TL_{c}-1\} dkc \\
	&	
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdkc} - 
		\gamma (\hat{pw}_{m-1dkc}  + E[pwt\_d_{m-1d-1c}] - E[pwt\_d_{d}] +\\ 
		& && \qquad + E[pwt\_k_{k-1}] - E[pwt\_k_{k}]) \Big) \ge E[pw_{mdkc}]
		&&	\forall m \in \{TL_{c}...M-1\} dkc \\
	&	
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{Mdc} - \gamma 
		\sum_{M-1}^{M} (\hat{pw}_{mdc} + E[pwt\_d_{md-1c}] - E[pwt\_d_{d}] + \\
		&	&& \qquad  + E[pwt\_k_{k-1k}] - E[pwt\_k_{k}] )  \Big) \ge E[pw_{Mdc}]
		&&	\forall dkc \\ 
	&	\beta^{ps}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{t0dkc} \Big) \ge E[ps_{t0dkc}]
		&&	\forall tdkc \\
	&	
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{Tmdkc} \Big) \ge E[ps_{Tmdkc}]
		&&	\forall mdkc \\
	&	
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdkc} - \gamma 
				(\hat{ps}_{t+1m-1dkc}) \Big) \ge E[ps_{tmdkc}] \;
		&&	\forall \{1...T-1\} \{1...TL_{c}-1\}dkc \\
	&	
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdkc} - \gamma 
				(\hat{ps}_{t+1m-1dc} + E[pst\_d_{t+1m-1d-1c}] - E[pst\_d_{d}] + \\
		& &&	+ E[pst\_k_{k-1}] - E[pst\_k_{k}]) \Big) \ge E[ps_{tmdkc}] 
		&&	\forall \{1...T-1\} \{TL_{c}...M-1\}dkc \\
	&	
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tMdkc} - \gamma \sum_{M-1}^{M}
				(\hat{ps}_{t+1mdkc} + E[pst\_d_{t+1md-1c}] - E[pst\_d_{d}] + \\
		& &&	+ E[pst\_k_{k-1}] - E[pst\_k_{k}]) \Big) \ge E[ps_{tMdkc}]
		&&	\forall \{1...T-1\} dkc
\end{alignat}

@@

\section{Solution Explanation}
\subsection{Algorithm for solving}
To get $\vec{\beta}$ values, which will be used to generate an action follow steps below:
\begin{enumerate}
	\item Perform a monte-carlo simulation (following some arbitrary policy) to get $E[ue], E[uu], E[pw] E[pw]$
	\item Create an initial feasible set of state-action pairs - $\vec{w}$
	\item Solve model in section "\nameref{Dual of ADP LP}" where each state-action pairs in $\vec{w}$ corresponds to a variable and parameters for all the constraints for a specific action.
	\item Solve model in section "\nameref{Pricing Problem}", where duals from problem in step 3  correspond to $\vec{\beta}$ values. 
	\begin{itemize}
		\item If objective function is less than 0, add solution as a single state-action pair to $\vec{w}$ and go to step 3
		\item If objective function is greater than 0, continue to next step
	\end{itemize}
	\item Duals from problem in step 3 correspond to final $\vec{\beta}$ values
\end{enumerate}

>>>>

\begin{alignat}{10}
	& \beta^{0}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} (1 - \gamma) = 1 \\
	& \beta^{ul}: 
		&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ul_{p} - 
		\gamma (\hat{ul}_{p}) \Big) \ge E[ul_{p}] 
		&&	\forall p \in p\_co \\ 
	&	
		&& 	\sum_{\vec{S}\vec{A}}\vec{w} ( ul_{p}) \ge E[ul_{p}]
		&&	\forall p \in p\_nco \\
	&	\beta^{pw}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{0dkc} - 
		\gamma (pea_{dkc}) \Big) \ge E[ps_{0dkc}]
		&&	\forall dkc \\
	&	
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdkc} - 
		\gamma (\hat{pw}_{m-1dkc}) \Big) \ge E[pw_{mdkc}]
		&&	\forall m \in \{1...TL_{c}-1\} dkc \\
	&	
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdkc} - 
		\gamma (\hat{pw}_{m-1dkc}  + E[pwt\_d_{m-1d-1c}] - E[pwt\_d_{d}] +\\ 
		& && \qquad + E[pwt\_k_{k-1}] - E[pwt\_k_{k}]) \Big) \ge E[pw_{mdkc}]
		&&	\forall m \in \{TL_{c}...M-1\} dkc \\
	&	
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{Mdkc} - \gamma 
		\sum_{M-1}^{M} (\hat{pw}_{mdkc} + E[pwt\_d_{md-1c}] - E[pwt\_d_{d}] + \\
		&	&& \qquad  + E[pwt\_k_{k-1k}] - E[pwt\_k_{k}] )  \Big) \ge E[pw_{Mdkc}]
		&&	\forall dkc \\ 
	&	\beta^{ps}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{t0dkc} \Big) \ge E[ps_{t0dkc}]
		&&	\forall tdkc \\
	&	
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{Tmdkc} \Big) \ge E[ps_{Tmdkc}]
		&&	\forall mdkc \\
	&	
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdkc} - \gamma 
				(\hat{ps}_{t+1m-1dkc}) \Big) \ge E[ps_{tmdkc}] \;
		&&	\forall \{1...T-1\} \{1...TL_{c}-1\}dkc \\
	&	
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdkc} - \gamma 
				(\hat{ps}_{t+1m-1dc} + E[pst\_d_{t+1m-1d-1c}] - E[pst\_d_{d}] + \\
		& &&	+ E[pst\_k_{k-1}] - E[pst\_k_{k}]) \Big) \ge E[ps_{tmdkc}] 
		&&	\forall \{1...T-1\} \{TL_{c}...M-1\}dkc \\
	&	
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tMdkc} - \gamma \sum_{M-1}^{M}
				(\hat{ps}_{t+1mdkc} + E[pst\_d_{t+1md-1c}] - E[pst\_d_{d}] + \\
		& &&	+ E[pst\_k_{k-1}] - E[pst\_k_{k}]) \Big) \ge E[ps_{tMdkc}]
		&&	\forall \{1...T-1\} dkc
\end{alignat}

@@

\section{Solution Explanation}
\subsection{Algorithm for solving}
To get $\vec{\beta}$ values, which will be used to generate an action follow steps below:
\begin{enumerate}
	\item Perform a monte-carlo simulation (following some arbitrary policy) to get $E[ul], E[pw] E[pw]$
	\item Create an initial feasible set of state-action pairs - $\vec{w}$
	\item Solve model in section "\nameref{Dual of ADP LP}" where each state-action pairs in $\vec{w}$ corresponds to a variable and parameters for all the constraints for a specific action.
	\item Solve model in section "\nameref{Pricing Problem}", where duals from problem in step 3  correspond to $\vec{\beta}$ values. 
	\begin{itemize}
		\item If objective function is less than 0, add solution as a single state-action pair to $\vec{w}$ and go to step 3
		\item If objective function is greater than 0, continue to next step
	\end{itemize}
	\item Duals from problem in step 3 correspond to final $\vec{\beta}$ values
\end{enumerate}
